Extract team means and SDs

### 2022-09-09 scripts/r/07_team-sds.Rmd
join df with relevant data from vars from google sheet

# Knitr options
knitr::opts_chunk$set(echo = TRUE, message = FALSE)

@@

# Means and SDs
anomalocaris_ornata_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "anomalocaris_ornata", 1, "intensity", mean(df.int$Mean_dB^2),        sd(df.int$Mean_dB^2), 
  "anomalocaris_ornata", 2, "f0",        mean(under$f0sem),             sd(under$f0sem), 
  "anomalocaris_ornata", 3, "f0",        mean(over$f0sem),              sd(over$f0sem), 
  "anomalocaris_ornata", 4, "duration",  mean(vowel.df$Duration_in_ms), sd(vowel.df$Duration_in_ms)
)

@@

# Means and SDs
anthracoceros_coronata_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "anthracoceros_coronata", 1, "f0",        mean(data_long$A_max_pitch),  sd(data_long$A_max_pitch), 
  "anthracoceros_coronata", 2, "f0",        mean(data_long$N_max_pitch, na.rm = T),  sd(data_long$N_max_pitch, na.rm = T), 
  "anthracoceros_coronata", 3, "intensity", mean(data_long$A_max_intens), sd(data_long$A_max_intens), 
  "anthracoceros_coronata", 4, "intensity", mean(data_long$N_max_intens), sd(data_long$N_max_intens), 
  "anthracoceros_coronata", 5, "duration",  mean(data_long$A_dur_log),    sd(data_long$A_dur_log), 
  "anthracoceros_coronata", 6, "duration",  mean(data_long$N_dur_log),    sd(data_long$N_dur_log), 
)

@@

# Means and SDs
arapaima_modularis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "arapaima_modularis", 1, "f0", mean(data_for_analysis_noOL$mean_pitch), sd(data_for_analysis_noOL$mean_pitch)
)

@@

# Means and SDs
clione_dorsalis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "clione_dorsalis", 1, "duration", mean(data_formant_midpoint$word.duration), sd(data_formant_midpoint$word.duration)
)

@@

# Means and SDs
comanthina_maculatus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "comanthina_maculatus", 1, "duration", mean(MSA_comanthina_maculatus_df$tonic_vowel_duration), sd(MSA_comanthina_maculatus_df$tonic_vowel_duration), 
  "comanthina_maculatus", 2, "intensity", mean(MSA_comanthina_maculatus_df$tonic_vowel_intensity), sd(MSA_comanthina_maculatus_df$tonic_vowel_intensity),  
  "comanthina_maculatus", 3, "f0", mean(MSA_comanthina_maculatus_df$tonic_vowel_F0), sd(MSA_comanthina_maculatus_df$tonic_vowel_F0), 
)

@@

# Means and SDs
cromileptes_saxatilis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "cromileptes_saxatilis", 1, "duration", mean(cromileptes_saxatilis_durs$colour_dur), sd(cromileptes_saxatilis_durs$colour_dur)
)

@@

# Means and SDs
gnathosaurus_canadensis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "gnathosaurus_canadensis", 1, "f0", mean(gnathosaurus_canadensis_typ$median_st_diff), sd(gnathosaurus_canadensis_typ$median_st_diff)
)

@@

# Means and SDs
gymnothorax_spinulosus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "gymnothorax_spinulosus", 1, "intensity", mean(gymnothorax_spinulosus_int$measure), sd(gymnothorax_spinulosus_int$measure)
)

@@

# Means and SDs
haematopus_fossor_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "haematopus_fossor", 1, "duration", mean(duration_full$framedur), sd(duration_full$framedur), 
  "haematopus_fossor", 2, "duration", mean(duration_full$adjdur), sd(duration_full$adjdur), 
  "haematopus_fossor", 3, "duration", mean(duration_full$noundur), sd(duration_full$noundur), 
  "haematopus_fossor", 4, "duration", mean(adj_full$duration), sd(adj_full$duration), 
  "haematopus_fossor", 5, "duration", mean(noun_full$duration), sd(noun_full$duration), 
  "haematopus_fossor", 6, "intensity", mean(adj_full$intensity), sd(adj_full$intensity), 
  "haematopus_fossor", 7, "intensity", mean(noun_full$intensity), sd(noun_full$intensity), 
)

@@

# Means and SDs
lasionycteris_altavela_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "lasionycteris_altavela", 1, "intensity", mean(intensity_DF$Intensity), sd(intensity_DF$Intensity),
)

@@

# Means and SDs
naso_cassivellaunos_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "naso_cassivellaunos", 1, "f0", mean(msa$DeltaF0_rel), sd(msa$DeltaF0_rel), 
  "naso_cassivellaunos", 2, "f0", mean(msa$sync_rel), sd(msa$sync_rel),
)

@@

# Means and SDs
psittacula_scabriculus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "psittacula_scabriculus", 1, "duration", mean(MSAcomplete$avgdur), sd(MSAcomplete$avgdur), 
)

@@

# Means and SDs
trapezia_cantonensis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "trapezia_cantonensis", 1, "duration", mean(MSA_trapezia_cantonensis_data$dur), sd(MSA_trapezia_cantonensis_data$dur), 
)

@@

# This part won't work because some coders refuse to use `here`
# source_part(
#  file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
#  start = 21, 
#  end = 32
#  )

@@

# Means and SDs
dermatolepis_aculeatus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "dermatolepis_aculeatus", 1, "f0", mean(msa_data$noun_pitch_max), sd(msa_data$noun_pitch_max), 
  "dermatolepis_aculeatus", 2, "f0", mean(msa_data$adj_pitch_max), sd(msa_data$adj_pitch_max), 
  "dermatolepis_aculeatus", 3, "f0", mean(msa_data$phrase_pitch_max), sd(msa_data$phrase_pitch_max), 
)

@@

# Means and SDs
eriphia_laterispinis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "eriphia_laterispinis", 1, "f0",        mean(msa_data$mean_f0), sd(msa_data$mean_f0), 
  "eriphia_laterispinis", 2, "intensity", mean(msa_data$mean_int), sd(msa_data$mean_int), 
  "eriphia_laterispinis", 3, "duration",  mean(msa_data$duration), sd(msa_data$duration), 
)

@@

# Means and SDs
hoplostethus_macrosteus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "hoplostethus_macrosteus", 1, "duration",  mean(msa_data$durmsec), sd(msa_data$durmsec), 
  "hoplostethus_macrosteus", 2, "intensity", mean(msa_data$intensity_maximum), sd(msa_data$intensity_maximum), 
)

@@

# Means and SDs
neosilurus_omanensis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "neosilurus_omanensis", 1, "f0", mean(msa_data$PitchRatioAtoU), sd(msa_data$PitchRatioAtoU), 
  "neosilurus_omanensis", 2, "f0", mean(msa_data$PitchRangeRatioAtoU), sd(msa_data$PitchRangeRatioAtoU), 
  "neosilurus_omanensis", 4, "f0", mean(msa_data$PitchRiseRatio), sd(msa_data$PitchRiseRatio), 
)

@@

# Means and SDs
nestor_idahoensis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "nestor_idahoensis", 1, "duration", mean(msa_data$duration), sd(msa_data$duration), 
  "nestor_idahoensis", 2, "f0",       mean(msa_data$f0), sd(msa_data$f0), 
)

@@

# Means and SDs
paralichthys_undulatus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "paralichthys_undulatus", 1, "f0", mean(msa_data$RangeST), sd(msa_data$RangeST), 
)

@@

# Means and SDs
petauroides_fistulator_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "petauroides_fistulator", 1, "f0", mean(msa_data$pitch_st), sd(msa_data$pitch_st), 
)

@@

# Means and SDs
saron_pictus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "saron_pictus", 1, "duration", mean(msa_data$dur_ms), sd(msa_data$dur_ms), 
)

@@

# Means and SDs
trachurus_riukiuensis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "trachurus_riukiuensis", 1, "duration", mean(data$art_dur), sd(data$art_dur),
  "trachurus_riukiuensis", 2, "f0", mean(article$art_peakf0), sd(article$art_peakf0),
  "trachurus_riukiuensis", 3, "duration", mean(data$adj_dur), sd(data$adj_dur), 
  "trachurus_riukiuensis", 4, "f0", mean(adjective$adj_peakf0), sd(adjective$adj_peakf0),
  "trachurus_riukiuensis", 5, "f0", mean(noun$noun_peakf0), sd(noun$noun_peakf0),
)

@@

# Means and SDs
varanus_eulophotes_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "varanus_eulophotes", 1, "f0", mean(msa_data$avgF0), sd(msa_data$avgF0), 
)

@@

# Means and SDs
alosa_atun_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "alosa_atun", 1,  "f0",        mean(MSA_finale$meanPitch), sd(MSA_finale$meanPitch), 
  "alosa_atun", 2,  "intensity", mean(MSA_finale$maxIntensity), sd(MSA_finale$maxIntensity), 
  "alosa_atun", 3,  "duration",  mean(MSA_finale$Target.segment.duration), sd(MSA_finale$Target.segment.duration), 
  "alosa_atun", 6,  "f0",        mean(MSA_finalschwa$meanPitch), sd(MSA_finalschwa$meanPitch), 
  "alosa_atun", 7,  "intensity", mean(MSA_finalschwa$maxIntensity), sd(MSA_finalschwa$maxIntensity), 
  "alosa_atun", 8,  "duration",  mean(MSA_finalschwa$Target.segment.duration), sd(MSA_finalschwa$Target.segment.duration), 
  "alosa_atun", 11, "duration",  mean(MSA_both$DiphDur), sd(MSA_both$DiphDur), 
  "alosa_atun", 12, "duration",  mean(MSA_both$DurRat), sd(MSA_both$DurRat), 
  "alosa_atun", 14, "duration",  mean(MSA_finale$Target.word.duration), sd(MSA_finale$Target.word.duration), 
  "alosa_atun", 15, "duration",  mean(MSA_finale$Pause.duration, na.rm = T), sd(MSA_finale$Pause.duration, na.rm = T), 
  "alosa_atun", 16, "duration",  mean(MSA_both$syllablesPerMinute), sd(MSA_both$syllablesPerMinute), 
)

@@

# Means and SDs
chelonia_brummeri_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "chelonia_brummeri", 1,  "duration",  mean(d$rel_dur), sd(d$rel_dur), 
  "chelonia_brummeri", 2,  "intensity", mean(d$rel_intens), sd(d$rel_intens), 
  "chelonia_brummeri", 3,  "f0",        mean(d$f0range_st), sd(d$f0range_st), 
  "chelonia_brummeri", 4,  "f0",        mean(d$adj_maxf0), sd(d$adj_maxf0), 
)

@@

# Means and SDs
dunkleosteus_inscriptus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "dunkleosteus_inscriptus", 1,  "duration", mean(dat$rel_n), sd(dat$rel_n), 
  "dunkleosteus_inscriptus", 2,  "duration", mean(dat$dur_n), sd(dat$dur_n), 
  "dunkleosteus_inscriptus", 3,  "duration", mean(dat$rel_a), sd(dat$rel_a), 
  "dunkleosteus_inscriptus", 4,  "duration", mean(dat$dur_a), sd(dat$dur_a), 
  "dunkleosteus_inscriptus", 5,  "duration", mean(dat$dur_np), sd(dat$dur_np),
)

@@

# Means and SDs
pervagor_meeki_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "pervagor_meeki", 1,  "intensity", mean(data_int_trim[data_int_trim$word_type == "target_name",]$Overall_Intensity), sd(data_int_trim[data_int_trim$word_type == "target_name",]$Overall_Intensity), 
  "pervagor_meeki", 2,  "duration", mean(data_dur_trim[data_dur_trim$word_type == "target_name",]$Duration_ms), sd(data_dur_trim[data_dur_trim$word_type == "target_name",]$Duration_ms), 
  "pervagor_meeki", 3,  "f0", mean(data_meanf0_trim[data_meanf0_trim$word_type == "target_name",]$Mean_f0_st), sd(data_meanf0_trim[data_meanf0_trim$word_type == "target_name",]$Mean_f0_st), 
  "pervagor_meeki", 4,  "f0", mean(data_maxf0_trim[data_maxf0_trim$word_type == "target_name",]$Max_f0_st), sd(data_maxf0_trim[data_maxf0_trim$word_type == "target_name",]$Max_f0_st), 
  "pervagor_meeki", 5,  "intensity", mean(data_int_trim[data_int_trim$word_type == "target_colour",]$Overall_Intensity), sd(data_int_trim[data_int_trim$word_type == "target_colour",]$Overall_Intensity), 
  "pervagor_meeki", 6,  "duration",  mean(data_dur_trim[data_dur_trim$word_type == "target_colour",]$Duration_ms), sd(data_dur_trim[data_dur_trim$word_type == "target_colour",]$Duration_ms),
  "pervagor_meeki", 7,  "f0", mean(data_meanf0_trim[data_meanf0_trim$word_type == "target_colour",]$Mean_f0_st), sd(data_meanf0_trim[data_meanf0_trim$word_type == "target_colour",]$Mean_f0_st),
  "pervagor_meeki", 8,  "f0", mean(data_maxf0_trim[data_maxf0_trim$word_type == "target_colour",]$Max_f0_st), sd(data_maxf0_trim[data_maxf0_trim$word_type == "target_colour",]$Max_f0_st),
)

@@

# Means and SDs
procambarus_mahogoni_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "procambarus_mahogoni", 1,  "duration",  mean(msa_data_raw$v1_duration_c), sd(msa_data_raw$v1_duration_c), 
  "procambarus_mahogoni", 2,  "f0",        mean(msa_data_raw$v1_pitch_mean_c), sd(msa_data_raw$v1_pitch_mean_c), 
  "procambarus_mahogoni", 3,  "intensity", mean(msa_data_raw$v1_int_mean_c), sd(msa_data_raw$v1_int_mean_c), 
)

@@

# Means and SDs
trachyphyllia_lappa_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "trachyphyllia_lappa", 1,  "duration", mean(duration_adj_data$duration), sd(duration_adj_data$duration), 
  "trachyphyllia_lappa", 2,  "f0",       mean(pitch_adj_data$maximum), sd(pitch_adj_data$maximum), 
  "trachyphyllia_lappa", 3,  "f0", mean(pitch_adj_data$minimum), sd(pitch_adj_data$minimum), 
  "trachyphyllia_lappa", 4,  "f0", mean(pitch_adj_data$range), sd(pitch_adj_data$range), 
  "trachyphyllia_lappa", 5,  "duration", mean(duration_noun_data$duration), sd(duration_noun_data$duration), 
  "trachyphyllia_lappa", 6,  "f0", mean(pitch_noun_data$maximum), sd(pitch_noun_data$maximum), 
  "trachyphyllia_lappa", 7,  "f0", mean(pitch_noun_data$minimum), sd(pitch_noun_data$minimum), 
  "trachyphyllia_lappa", 8,  "f0", mean(pitch_noun_data$range), sd(pitch_noun_data$range), 
)

>>>>

# Knitr options
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE
  )

knitr::opts_knit$set(root.dir = here::here())

@@

# Means and SDs
anomalocaris_ornata_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "anomalocaris_ornata", 1, "intensity", mean(df.int$Mean_dB),        sd(df.int$Mean_dB), 
  "anomalocaris_ornata", 2, "f0",        mean(under$f0sem),             sd(under$f0sem), 
  "anomalocaris_ornata", 3, "f0",        mean(over$f0sem),              sd(over$f0sem), 
  "anomalocaris_ornata", 4, "duration",  mean(vowel.df$Duration_in_ms), sd(vowel.df$Duration_in_ms)
)

@@

# Means and SDs
anthracoceros_coronata_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "anthracoceros_coronata", 1, "f0",        mean(data_long$A_max_pitch),  sd(data_long$A_max_pitch), 
  "anthracoceros_coronata", 2, "f0",        mean(data_long$N_max_pitch, na.rm = T),  sd(data_long$N_max_pitch, na.rm = T), 
  "anthracoceros_coronata", 3, "intensity", mean(data_long$A_max_intens), sd(data_long$A_max_intens), 
  "anthracoceros_coronata", 4, "intensity", mean(data_long$N_max_intens), sd(data_long$N_max_intens), 
  "anthracoceros_coronata", 5, "duration",  mean(data_long$A_dur_log),    sd(data_long$A_dur_log), 
  "anthracoceros_coronata", 6, "duration",  mean(data_long$N_dur_log),    sd(data_long$N_dur_log), 
)

@@

# Means and SDs
arapaima_modularis_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "arapaima_modularis", 1, "f0", mean(data_for_analysis_noOL$mean_pitch), sd(data_for_analysis_noOL$mean_pitch)
)

@@

# Means and SDs
clione_dorsalis_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "clione_dorsalis", 1, "duration", mean(data_formant_midpoint$word.duration), sd(data_formant_midpoint$word.duration)
)

@@

# Means and SDs
comanthina_maculatus_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "comanthina_maculatus", 1, "duration", mean(MSA_comanthina_maculatus_df$tonic_vowel_duration), sd(MSA_comanthina_maculatus_df$tonic_vowel_duration), 
  "comanthina_maculatus", 2, "intensity", mean(MSA_comanthina_maculatus_df$tonic_vowel_intensity), sd(MSA_comanthina_maculatus_df$tonic_vowel_intensity),  
  "comanthina_maculatus", 3, "f0", mean(MSA_comanthina_maculatus_df$tonic_vowel_F0), sd(MSA_comanthina_maculatus_df$tonic_vowel_F0), 
)

@@

# Means and SDs
cromileptes_saxatilis_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "cromileptes_saxatilis", 1, "duration", mean(cromileptes_saxatilis_durs$colour_dur), sd(cromileptes_saxatilis_durs$colour_dur)
)

@@

# Means and SDs
gnathosaurus_canadensis_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "gnathosaurus_canadensis", 1, "f0", mean(gnathosaurus_canadensis_typ$median_st_diff), sd(gnathosaurus_canadensis_typ$median_st_diff)
)

@@

# Means and SDs
gymnothorax_spinulosus_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "gymnothorax_spinulosus", 1, "intensity", mean(gymnothorax_spinulosus_int$measure), sd(gymnothorax_spinulosus_int$measure)
)

@@

# Means and SDs
haematopus_fossor_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "haematopus_fossor", 1, "duration", mean(duration_full$framedur), sd(duration_full$framedur), 
  "haematopus_fossor", 2, "duration", mean(duration_full$adjdur), sd(duration_full$adjdur), 
  "haematopus_fossor", 3, "duration", mean(duration_full$noundur), sd(duration_full$noundur), 
  "haematopus_fossor", 4, "duration", mean(adj_full$duration), sd(adj_full$duration), 
  "haematopus_fossor", 5, "duration", mean(noun_full$duration), sd(noun_full$duration), 
  "haematopus_fossor", 6, "intensity", mean(adj_full$intensity), sd(adj_full$intensity), 
  "haematopus_fossor", 7, "intensity", mean(noun_full$intensity), sd(noun_full$intensity), 
)

@@

# Means and SDs
lasionycteris_altavela_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "lasionycteris_altavela", 1, "intensity", mean(intensity_DF$Intensity), sd(intensity_DF$Intensity),
)

@@

# Means and SDs
naso_cassivellaunos_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "naso_cassivellaunos", 2, "f0", mean(msa$DeltaF0_rel), sd(msa$DeltaF0_rel), 
  "naso_cassivellaunos", 3, "f0", mean(msa$sync_rel), sd(msa$sync_rel),
)

@@

# Means and SDs
psittacula_scabriculus_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "psittacula_scabriculus", 1, "duration", mean(MSAcomplete$avgdur), sd(MSAcomplete$avgdur), 
)

@@

# Means and SDs
trapezia_cantonensis_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "trapezia_cantonensis", 4, "duration", mean(MSA_trapezia_cantonensis_data$dur), sd(MSA_trapezia_cantonensis_data$dur), 
)

@@

source_part(
 file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
 start = 21, 
 end = 32
)

@@

# Means and SDs
dermatolepis_aculeatus_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "dermatolepis_aculeatus", 1, "f0", mean(msa_data$noun_pitch_max), sd(msa_data$noun_pitch_max), 
  "dermatolepis_aculeatus", 2, "f0", mean(msa_data$adj_pitch_max), sd(msa_data$adj_pitch_max), 
  "dermatolepis_aculeatus", 3, "f0", mean(msa_data$phrase_pitch_max), sd(msa_data$phrase_pitch_max), 
)

@@

# Means and SDs
eriphia_laterispinis_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "eriphia_laterispinis", 1, "f0",        mean(msa_data$mean_f0), sd(msa_data$mean_f0), 
  "eriphia_laterispinis", 1, "intensity", mean(msa_data$mean_int), sd(msa_data$mean_int), 
  "eriphia_laterispinis", 1, "duration",  mean(msa_data$duration), sd(msa_data$duration), 
)

@@

# Means and SDs
hoplostethus_macrosteus_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "hoplostethus_macrosteus", 1, "duration",  mean(msa_data$durmsec), sd(msa_data$durmsec), 
  "hoplostethus_macrosteus", 2, "intensity", mean(msa_data$intensity_maximum), sd(msa_data$intensity_maximum), 
)

@@

# Means and SDs
neosilurus_omanensis_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "neosilurus_omanensis", 1, "f0", mean(msa_data$PitchRatioAtoU), sd(msa_data$PitchRatioAtoU), 
  "neosilurus_omanensis", 2, "f0", mean(msa_data$PitchRangeRatioAtoU), sd(msa_data$PitchRangeRatioAtoU), 
  "neosilurus_omanensis", 4, "f0", mean(msa_data$PitchRiseRatio), sd(msa_data$PitchRiseRatio), 
)

@@

# Means and SDs
nestor_idahoensis_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "nestor_idahoensis", 1, "duration", mean(msa_data$duration), sd(msa_data$duration), 
  "nestor_idahoensis", 1, "f0",       mean(msa_data$f0), sd(msa_data$f0), 
)

@@

# Means and SDs
paralichthys_undulatus_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "paralichthys_undulatus", 1, "f0", mean(msa_data$RangeST), sd(msa_data$RangeST), 
)

@@

# Means and SDs
petauroides_fistulator_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "petauroides_fistulator", 1, "f0", mean(msa_data$pitch_st), sd(msa_data$pitch_st), 
)

@@

# Means and SDs
saron_pictus_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "saron_pictus", 1, "duration", mean(msa_data$dur_ms), sd(msa_data$dur_ms), 
)

@@

# Means and SDs
trachurus_riukiuensis_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "trachurus_riukiuensis", 1, "duration", mean(data$art_dur), sd(data$art_dur),
  "trachurus_riukiuensis", 2, "f0", mean(article$art_peakf0), sd(article$art_peakf0),
  "trachurus_riukiuensis", 3, "duration", mean(data$adj_dur), sd(data$adj_dur), 
  "trachurus_riukiuensis", 4, "f0", mean(adjective$adj_peakf0), sd(adjective$adj_peakf0),
  "trachurus_riukiuensis", 5, "f0", mean(noun$noun_peakf0), sd(noun$noun_peakf0),
)

@@

# Means and SDs
varanus_eulophotes_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "varanus_eulophotes", 1, "f0", mean(msa_data$avgF0), sd(msa_data$avgF0), 
)

@@

# Means and SDs
alosa_atun_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "alosa_atun", 1,  "f0",        mean(MSA_finale$meanPitch), sd(MSA_finale$meanPitch), 
  "alosa_atun", 2,  "intensity", mean(MSA_finale$maxIntensity), sd(MSA_finale$maxIntensity), 
  "alosa_atun", 3,  "duration",  mean(MSA_finale$Target.segment.duration), sd(MSA_finale$Target.segment.duration), 
  "alosa_atun", 6,  "f0",        mean(MSA_finalschwa$meanPitch), sd(MSA_finalschwa$meanPitch), 
  "alosa_atun", 7,  "intensity", mean(MSA_finalschwa$maxIntensity), sd(MSA_finalschwa$maxIntensity), 
  "alosa_atun", 8,  "duration",  mean(MSA_finalschwa$Target.segment.duration), sd(MSA_finalschwa$Target.segment.duration), 
  "alosa_atun", 11, "duration",  mean(MSA_both$DiphDur), sd(MSA_both$DiphDur), 
  "alosa_atun", 12, "duration",  mean(MSA_both$DurRat), sd(MSA_both$DurRat), 
  "alosa_atun", 14, "duration",  mean(MSA_finale$Target.word.duration), sd(MSA_finale$Target.word.duration), 
  "alosa_atun", 15, "duration",  mean(MSA_finale$Pause.duration, na.rm = T), sd(MSA_finale$Pause.duration, na.rm = T), 
  "alosa_atun", 16, "duration",  mean(MSA_both$syllablesPerMinute), sd(MSA_both$syllablesPerMinute), 
)

@@

# Means and SDs
chelonia_brummeri_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "chelonia_brummeri", 1,  "duration",  mean(d$rel_dur), sd(d$rel_dur), 
  "chelonia_brummeri", 2,  "intensity", mean(d$rel_intens), sd(d$rel_intens), 
  "chelonia_brummeri", 3,  "f0",        mean(d$f0range_st), sd(d$f0range_st), 
  "chelonia_brummeri", 4,  "f0",        mean(d$adj_maxf0), sd(d$adj_maxf0), 
)

@@

# Means and SDs
dunkleosteus_inscriptus_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "dunkleosteus_inscriptus", 1,  "duration", mean(dat$rel_n), sd(dat$rel_n), 
  "dunkleosteus_inscriptus", 2,  "duration", mean(dat$dur_n), sd(dat$dur_n), 
  "dunkleosteus_inscriptus", 3,  "duration", mean(dat$rel_a), sd(dat$rel_a), 
  "dunkleosteus_inscriptus", 4,  "duration", mean(dat$dur_a), sd(dat$dur_a), 
  "dunkleosteus_inscriptus", 5,  "duration", mean(dat$dur_np), sd(dat$dur_np),
)

@@

# Means and SDs
pervagor_meeki_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "pervagor_meeki", 1,  "intensity", mean(data_int_trim[data_int_trim$word_type == "target_name",]$Overall_Intensity), sd(data_int_trim[data_int_trim$word_type == "target_name",]$Overall_Intensity), 
  "pervagor_meeki", 2,  "duration", mean(data_dur_trim[data_dur_trim$word_type == "target_name",]$Duration_ms), sd(data_dur_trim[data_dur_trim$word_type == "target_name",]$Duration_ms), 
  "pervagor_meeki", 3,  "f0", mean(data_meanf0_trim[data_meanf0_trim$word_type == "target_name",]$Mean_f0_st), sd(data_meanf0_trim[data_meanf0_trim$word_type == "target_name",]$Mean_f0_st), 
  "pervagor_meeki", 4,  "f0", mean(data_maxf0_trim[data_maxf0_trim$word_type == "target_name",]$Max_f0_st), sd(data_maxf0_trim[data_maxf0_trim$word_type == "target_name",]$Max_f0_st), 
  "pervagor_meeki", 5,  "intensity", mean(data_int_trim[data_int_trim$word_type == "target_colour",]$Overall_Intensity), sd(data_int_trim[data_int_trim$word_type == "target_colour",]$Overall_Intensity), 
  "pervagor_meeki", 6,  "duration",  mean(data_dur_trim[data_dur_trim$word_type == "target_colour",]$Duration_ms), sd(data_dur_trim[data_dur_trim$word_type == "target_colour",]$Duration_ms),
  "pervagor_meeki", 7,  "f0", mean(data_meanf0_trim[data_meanf0_trim$word_type == "target_colour",]$Mean_f0_st), sd(data_meanf0_trim[data_meanf0_trim$word_type == "target_colour",]$Mean_f0_st),
  "pervagor_meeki", 8,  "f0", mean(data_maxf0_trim[data_maxf0_trim$word_type == "target_colour",]$Max_f0_st), sd(data_maxf0_trim[data_maxf0_trim$word_type == "target_colour",]$Max_f0_st),
)

@@

# Means and SDs
procambarus_mahogoni_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "procambarus_mahogoni", 1,  "duration",  mean(msa_data_raw$v1_duration_c), sd(msa_data_raw$v1_duration_c), 
  "procambarus_mahogoni", 2,  "f0",        mean(msa_data_raw$v1_pitch_mean_c), sd(msa_data_raw$v1_pitch_mean_c), 
  "procambarus_mahogoni", 3,  "intensity", mean(msa_data_raw$v1_int_mean_c), sd(msa_data_raw$v1_int_mean_c), 
)

@@

# Means and SDs
trachyphyllia_lappa_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "trachyphyllia_lappa", 1,  "duration", mean(duration_adj_data$duration), sd(duration_adj_data$duration), 
  "trachyphyllia_lappa", 2,  "f0",       mean(pitch_adj_data$maximum), sd(pitch_adj_data$maximum), 
  "trachyphyllia_lappa", 3,  "f0", mean(pitch_adj_data$minimum), sd(pitch_adj_data$minimum), 
  "trachyphyllia_lappa", 4,  "f0", mean(pitch_adj_data$range), sd(pitch_adj_data$range), 
  "trachyphyllia_lappa", 5,  "duration", mean(duration_noun_data$duration), sd(duration_noun_data$duration), 
  "trachyphyllia_lappa", 6,  "f0", mean(pitch_noun_data$maximum), sd(pitch_noun_data$maximum), 
  "trachyphyllia_lappa", 7,  "f0", mean(pitch_noun_data$minimum), sd(pitch_noun_data$minimum), 
  "trachyphyllia_lappa", 8,  "f0", mean(pitch_noun_data$range), sd(pitch_noun_data$range), 
)
